Preregistration

### 2021-04-14 preregistration.Rmd
add classic power plot

library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

res_interval <- res %>%
  select(n_obs, std_estimate, mod_load, mod_int) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs, mod_load, mod_int) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop") %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower), list(smooth = ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE)))) %>% 
  ungroup()
```

```{r}
plot_interval <- res_interval %>% 
  ggplot(aes(n_obs, ymin = lower, ymax = upper, fill = alpha, group = alpha)) + 
  geom_ribbon() +
  scale_fill_viridis_c() +
  scale_y_continuous(breaks = seq(-0.2, 0.7, .1)) +
  theme_minimal()

plot_interval

plot_interval %+% aes(ymin = lower_smooth, ymax = upper_smooth)
```

```{r}
plot_width <- res_interval %>% 
  ggplot(aes(n_obs, width, color = alpha, group = alpha)) +
  geom_line() +
  scale_color_viridis_c() +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  theme(axis.text.x = element_text(angle = -90)) +
  NULL
plot_width
plot_width %+% aes(y = width_smooth)
```
```{r}
res_interval %>% 
  ggplot(aes(n_obs, width, color = alpha, group = alpha)) +
  geom_smooth(se = FALSE, span = .1, size = .5) +
  scale_color_viridis_c() +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  theme(axis.text.x = element_text(angle = -90)) +
  NULL
```

>>>>

library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
library(patchwork)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

res_interval <- res %>%
  select(n_obs, std_estimate, mod_load, mod_int) %>% 
  filter(!is.na(std_estimate)) %>% 
  group_by(n_obs, mod_load, mod_int) %>% 
  summarise(interval = list(interval(std_estimate, seq(0.05, .2, 0.01))), 
            .groups = "drop", median = median(std_estimate)) %>% 
  unnest(c(interval)) %>% 
  mutate(width = upper - lower, perc = 1 - alpha) %>% 
  group_by(alpha) %>% 
  arrange(n_obs) %>% 
  mutate(across(c(width, upper, lower),
                ~slide_dbl(.x, mean, na.rm = TRUE, .before = 2, .after = 0, .complete = FALSE))) %>% 
  ungroup() %>% 
  arrange(perc)
```

```{r}
minn <- filter(res_interval, perc == .8, width < .2) %>% 
  filter(n_obs == min(n_obs))
```

```{r}
plot_interval <- res_interval %>%
  ggplot(aes(
    n_obs,
    ymin = lower,
    ymax = upper,
    fill = perc,
    group = alpha
  )) +
  geom_ribbon() +
  geom_line(aes(y = median), color = "white") +
  geom_hline(yintercept = .2, linetype = "dotted") +
  scale_fill_viridis_c(
    begin = 1,
    end = 0,
    breaks  = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  scale_y_continuous(n.breaks = 10) +
  scale_x_continuous(breaks = seq(0, params$nmax, params$nstep * 10)) +
  theme_minimal() +
  labs(x = "N per Group", y = "Standardized Effect Size") +
  theme(legend.title = element_blank()) +
  NULL
```

```{r}
plot_width <- res_interval %>%
  ggplot(aes(n_obs, width, color = perc, group = perc)) +
  geom_line() +
  geom_point(
    data = minn,
    size = 3,
    color = "black",
    shape = 3
  ) +
  scale_color_viridis_c(
    begin = 1,
    end = 0,
    breaks = 1 - seq(0.05, .2, 0.05),
    labels = . %>% scales::percent(accuracy = 1)
  ) +
  theme_minimal() +
  scale_y_log10(breaks = seq(0, 0.8, .1)) +
  scale_x_continuous(breaks = seq(0, params$nmax, params$nstep * 10)) +
  labs(x = "N per Group", y = "Width of quantile\n(Standardized Effect Size)") +
  theme(legend.title = element_blank()) +
  NULL
```

```{r}
plot_interval +
  theme(axis.text.x = element_blank(), axis.title.x = element_blank()) + 
  plot_width +
  plot_layout(nrow = 2, guides = 'collect') +
  plot_annotation(tag_levels = 'A')
ggsave("plot.svg", device = svglite::svglite, width = 7, height = 4)
```

Plot A depicts the range of effectsizes we observed in the simulation, where the color encodes the density.
The light yellow interval shows where 80% of the estimates land.
The dotted line represents the simulated true effect size; the white line shows the median of observed effect sizes.

Plot B represents the width of the interval shown in Plot A on a logarithmic scale.
The cross shows the minimal required sample size so that 80% of the estimates land in a range of +/- .1.

```{r}
alpha <- seq(0.05, .2, 0.01)
res %>% 
  group_by(n_obs) %>% 
  summarise(power = list(tibble(alpha = alpha,
            power = map_dbl(alpha/2, ~mean(lrt_p < .x, na.rm = TRUE))))) %>% 
  unnest(power) %>% 
  ggplot(aes(n_obs, power, color = alpha, group = alpha)) +
  geom_line() +
  scale_color_viridis_c() +
  theme_minimal()
```
